Music Recommendation System Using the Million Song Dataset

### 2015-05-07 writeup/MSDgroupwriteup.tex

In order to tackle the issue of using implicit user feedback, we tried four different scaling schemas independently. These included normalizing user play counts by the total number of plays for the user, normalizing song play counts by the total number of plays for the song, making the data binary (changing all non-zero play counts to 1), and  applying tf-idf. While testing out these schemas, we continued to vary the hyper-parameters, $d$ and variance, in order to determine if they changed the MAP results significantly.

@@

Regardless, the best result achieved for PMF in the end was 0.0143 which was only slightly above the popularity baseline. Based on literature review, we have found that this is better or in line with what other people have achieved with using PMF on play counts. Nevertheless, this indicates that PMF is not suitable for the MSD dataset and this can be attributed to the implicit feedback issue or simply to the fact that the dataset is too sparse. However, it is still possible to apply matrix factorization techniques to this dataset through using metadata and this has been demonstrated to be viable by \citep{liangcodebook} which achieved MAP values exceeding 0.1.

>>>>

In order to tackle the issue of using implicit user feedback, we tried four different scaling schemas independently. These included normalizing user play counts by the total number of plays for the user, normalizing song play counts by the total number of plays for the song, making the data binary (changing all non-zero play counts to 1), and  applying tf-idf. While testing out these schemas, we continued to vary the hyper-parameters (i.e. $d$ and variance) in order to determine if they changed the MAP results significantly.

@@

Regardless, the best result achieved for PMF in the end was 0.0143, which was only slightly above the popularity baseline. Based on literature review, we have found that this is better or in line with what others have achieved with using PMF on play counts. Nevertheless, this indicates that PMF is not suitable for the MSD dataset and this can be attributed to the implicit feedback issue or simply to the fact that the dataset is too sparse. However, it is still possible to apply matrix factorization techniques to this dataset through using metadata and this has been demonstrated to be viable by \citet{liangcodebook} which achieved MAP values exceeding 0.1.
